Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/intro.tex
GPU pipeline architecture was described in enough detail to require a citation.

Programs featuring this structure are particularly important in real-time
computer graphics; in fact, modern graphics architectures \emph{require} that
graphics computations be organized into distinct {\em passes} which perform
increasingly fine-grained computations (for example, per object, per region of
the screen, and per pixel, where many computations in later passes use the
results from a single computation in an earlier pass).

>>>>

Programs featuring this structure are particularly important in real-time
computer graphics; in fact, modern graphics architectures \emph{require} that
graphics computations be organized into distinct {\em passes} which perform
increasingly fine-grained computations (for example, per object, per region of
the screen, and per pixel, where many computations in later passes use the
results from a single computation in an earlier pass)\,\cite{OpenGL4Spec}.
